\documentclass[]{cover}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{Soorej Santhoshkumar Nair}{ \urlstyle{same} \href{mailto:soorej.s.nair@gmail.com}{soorej.s.nair@gmail.com} | +1(303)243-2932 | \urlstyle{same}\href{https://github.com/Soorej30}{Github} | \urlstyle{same}\href{https://www.linkedin.com/in/soorej-s-nair-73559470/}{Linkedin}
}

\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{Expedition Technology (EXP)}
\companyaddress{
Hiring Committee,

}

\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear Recruiter,}

\lettercontent{I am writing to express my enthusiastic interest in the Summer Internship in Digital Signal Processing and Machine Learning position at Expedition Technology (EXP), which I discovered on LinkedIn. As a highly motivated and detail-oriented individual with a strong background in machine learning, digital signal processing, and programming, I believe I would be an excellent fit for this role.}

\lettercontent{With a Master's degree in Data Science from the University of Colorado Boulder, commencing in August 2025, and a Bachelor's degree with honors in Computer Science from Birla Institute of Technology and Science (BITS) Pilani, I possess a solid foundation in both theoretical and practical aspects of machine learning and digital signal processing. My extensive experience as a Senior Data Scientist at XPO, where I developed a Random Forest classifier-based customer-level churn classification and prediction model with an accuracy of 90\% on top 30\% confident predictions, has honed my skills in programming languages like Python and my proficiency in utilizing cloud run and Vertex AI pipelines to automate model training and prediction. Furthermore, my experience with designing and implementing computer vision-based solutions for extracting text and key fields from bills of lading at XPO has given me a strong familiarity with command-line interfaces and version control using Git. My skills in machine learning, neural networks, fuzzy logic, information retrieval, and image processing will enable me to effectively tackle the challenges presented by this internship.}

\lettercontent{I would like to express my sincere gratitude for considering my application for this exciting opportunity at Expedition Technology (EXP). I am confident that my skills, experience, and passion for digital signal processing and machine learning make me an ideal candidate for this position. Thank you for your time and consideration, and I look forward to the opportunity to discuss how my qualifications align with the requirements of this internship.}
\vspace{0.5cm}

\closing{Sincerely,}

\signature{Soorej Santhoshkumar Nair}
{+(303)243-2932 | }
{soorej.s.nair@gmail.com}

\end{document}  
\documentclass[]{article}